A Large and Variable Leading Tail of Helium in a Sub-Saturn Undergoing Runaway Inflation

### 2023-07-13 paper/paper1/ms.tex
Recenter figure to show absence of leading tail and delete paragraph-- reasonable but does not add too much

\begin{figure}
    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p3.png}
    \caption{Schematic of Keplerian orbital shear.  Locations outside the Roche lobe experience orbital shear from the Keplerian potential.  A wind launched primarily from the dayside will tend to form a leading tail.}
    \label{fig:KeplerianShear}
\end{figure}

Stellar wind confinement \citep{2022ApJ...926..226M} arises from a bow-shock configuration, in which the planetary wind encounters the stellar wind and a shock front causes a density enhancement.  A trailing tail may also be present, but may not undergo the same boost in density, and could be rapidly carried away alongside the stellar wind.  A stellar-wind-induced asymmetry could result, yielding the appearance of a leading or trailing tail even if mass loss proceeds isotropically at first. Examples of this asymmetry can be seen in 3D MHD modeling of WASP 107~b \citep{2022ApJ...926..226M}.

>>>>

\begin{figure}
    \includegraphics[width=0.8\linewidth]{figures/KeplerianShear_v0p5_alt.png}
    \caption{Schematic of Keplerian orbital shear.  Locations outside the Roche lobe experience orbital shear from the Keplerian potential.  A wind launched primarily from the dayside will tend to form a leading tail.}
    \label{fig:KeplerianShear}
\end{figure}
